method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update method.Rmd

*Effects of emotion regulation on arousal and effort* <br> To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
<!-- @Anne please check! =) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
<!-- @Anne please check! =) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
<!-- perhaps alsway mention which r package will be used to run these proceudres -->
*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, the resulting (monetary) value will be divided by 2.00 €.
The final SV for each participant will be computed by averaging all final SVs of each strategy.
The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
Again, estimated, marginal means will be computed as post-hoc contrasts.

@@

To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
First, ER strategies will be re-coded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological arousal (*corrugator* activity and *levator* activity) as level-1-predictor will be specified.
$$
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
$$ Level-1-predictors will be centered within cluster [@Enders2007].
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), $\rho$, will be reported for each model (null model, as well as full model).

The influence of personality traits on SVs will be investigated exploratorily.
Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
<!--CS: Weitere Persönlichkeitsfaktoren ins Modell? Würde sagen erstmal nicht, denn sonst wird es a) überladen mit Prädiktoren und b) haben wir sonst kein Maß, was meiner Meinung nach mit ALLEN SVs zusammenhängen sollte. -->

The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threir FlexER score.
Therefore, SVs will be ordered by magnitude firstly.
Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? -->

For each result of the analyses both, $p$-values and Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021], will be reported.

>>>>

*Effects of emotion regulation on arousal and effort* <br> To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA will be conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing will be conducted for EMG activity of *corrugator* and *levator*.
<!-- @Anne please check! =) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) will be conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
<!-- @Anne please check! =) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
<!-- perhaps alsway mention which r package will be used to run these proceudres -->
*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.<!-- why exactly this value? -->
Second, the resulting (monetary) value will be divided by 2.00 €.
The final SV for each participant will be computed by averaging all final SVs of each strategy.
The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
Again, estimated, marginal means will be computed as post-hoc contrasts.

@@

To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological arousal (*corrugator* activity and *levator* activity) as level-1-predictor will be specified.
$$
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
$$ Level-1-predictors will be centered within cluster [@Enders2007].
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), $\rho$, will be reported for each model (null model, as well as full model).

The influence of personality traits on SVs will be investigated exploratorily.
Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
<!--CS: Weitere Persönlichkeitsfaktoren ins Modell? Würde sagen erstmal nicht, denn sonst wird es a) überladen mit Prädiktoren und b) haben wir sonst kein Maß, was meiner Meinung nach mit ALLEN SVs zusammenhängen sollte. Anm. AS: Ja, erstmal so schlank wie möglic halten. -->

The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threir FlexER score.
Therefore, SVs will be ordered by magnitude firstly.
Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? AS: Mir ehrlich gesagt erstmal nicht so ... -->

For each result of the analyses both, $p$-values and Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021], will be reported. Bayses factors are calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*. <!-- bzw welche Funktionen auch immer Du nutzt, hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->
